---
title: "Comparison of Two Data Sets"
output: html_notebook
---

```{r, echo = FALSE}
# Instructions:
# 1. Set data link correctly
# 2. Identify the two components: A = Old, B = New
# 3. Complete background section.

```


```{r, warning=FALSE}
# Packages ---------------------------------------------------------------
library(equivalence)
library(dplyr)
library(readxl)
library(tidyr)
library(ggplot2)

```


```{r}
#Identify incoming data:
data.in <- read_excel("W:/Quality Management System/Validation and Verification of methods/Chemistry/Project 203 - Investigation of the PV Room Lighting/PVAL01 comparisons.xlsx", 
    skip = 2)
data.in$A <- data.in$`without light`
data.in$B <- data.in$`with light`
An <- "Without_Light"
Bn <- "With_Light"
```



```{r}
#Clean up data to remove non-numberics:
data.in$A <- sapply(data.in$A, as.numeric)
data.in$B <- sapply(data.in$B, as.numeric)
data.in <- na.omit(data.in)
data.in$row_no <- as.numeric(rownames(data.in))

```

### Background ###




### Data Spread ###

Plot histogram of the original data set, to see data spread:

```{r}
hist(data.in$A, 
     main = paste("Histogram of ",An),
     breaks = 30,
     col = "cornflowerblue",
     xlab = "Level, g/100g")
```

Filter the data to remove outlying data and create the difference value. Two high results but leave them in for the moment. 

```{r}

data.in2 <- data.in %>%
        filter(A < 0.5) %>%
        mutate(Diff = B-A)

```


Plot the difference between the new and old methods:

```{r}
# Plot difference --------------------------------------------------------
ave_diff <- mean(abs(data.in2$Diff))

diff_plot <- ggplot(data.in2, aes(x=row_no, y = Diff)) +
        geom_segment(aes(xend = row_no), yend = 0)+
        geom_point(size = 4, shape = 21, col = "blue", fill = "cornflowerblue") +
        geom_hline(yintercept = 0)+
        theme_bw() +
        theme(axis.line = element_line(size = 0.7, color = "black"), 
              text = element_text(size = 14)) +
        labs(x="Test ID", y="Difference, mg/100g",  title= "Difference between the old test and the new\n")
diff_plot
```
Remove any outliers before proceding.  In the above plot, point 5 is suspect.

```{r}
data.in2 <- data.in2 %>%
        filter(Diff <0.1)
```



Least squares fit

```{r}
fit <- lm(data.in2$B~data.in2$A)
summary(fit)

```
The above printout of the least squares calculation gives a slope of 0.9777, an intercept of 0.0956 and an R2 of 0.9994.

```{r}
confint(fit)
```
When the 95% confidence interval is included around the slope and intercept it can be seen that both are significant: The slope range does not include 1 and the intercept does not include 0.  However the following plot indicates that these issues are more theoretical than practical.

### Plot Values ###

```{r}

vitc_plot <- ggplot(data.in2, aes(x=A, y=B)) +
        geom_point(size = 4, shape = 21, fill = "bisque", col = "cornflowerblue") +
        geom_smooth(method = lm) +
        geom_abline(slope = 1, intercept = 0, lty = 2, colour = "red") +
        labs(x = An,y = Bn) +
        theme_bw() +
        theme(axis.line = element_line(size = 0.7, color = "black"), 
              text = element_text(size = 14))

vitc_plot
```

To further explore the differences, a TOST test is performed.

### Two One-sided t Tests (TOST) ###

Nominal difference = 0.1

```{r}
vitc_tost <- tost(data.in2$A, data.in2$B, paired = TRUE, epsilon = 0.1)
vitc_tost
```

The Ho, that there is a difference between the two data sets is rejected if the epislon, tolerable differnce, is acceptable.  That is, there is not enough information to say that they are different.

To get an idea of what differnce in the results would be significant, a series of TOST tests is done and plotted:

```{r}

n=0.0
data_tost2 <- rep(0,100)
data_m <- rep(0,100)

for(i in 1:100){
        m = n + i*0.005
        tost_data <- tost(data.in2$A, data.in2$B, paired = TRUE, epsilon = m)
        data_tost2[i] <- tost_data$tost.p.value
        data_m[i] <- m
}

data3 <- as.data.frame(cbind(data_m,data_tost2))

# Plot p values ----------------------------------------------------------

plot_epsilon <- ggplot(data3, aes(x=data_m, y=data_tost2)) +
        geom_point() +
        geom_hline(yintercept = 0.05, col = "red", lty = 2) +
        theme_bw() +
        theme(axis.line = element_line(size = 0.7, color = "black"), 
              text = element_text(size = 14))
plot_epsilon

```

From the chart, it can be seen that the significance threshold is about 0.8.  A closer (iterative) estimate is: 
```{r, message=FALSE, echo=FALSE}
data_05 <- data3 %>%
        filter(data_tost2 >0.05) %>%
        top_n(-1)


data_06 <- data3 %>%
        filter(data_tost2 <0.05) %>%
        top_n(1)

data_07 <- rbind(data_05,data_06)



```
```{r}
limit <- data_07[1,1] + (data_07[2,1]-data_07[1,1]) * (data_07[1,2]-0.05)/(data_07[1,2]-data_07[2,2])
limit
```


































